\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

\title{Pixel Information of Images  using GIMP}

\author{Sumish Pal Singh Ajmani , Pascal Lafourcade}

\date{\today}

\begin{document}
\maketitle

\begin{abstract}
Your abstract.
\end{abstract}

\section{Information}

\begin{itemize}
\item For "no dot left aligned header": pixel coordinates for placing dot 217,112. Selected paintbrush tool( on left side) with black color and size 20.00 with 2. Hardness (51x51)( on right side)  image size chosen random 871x558 can de decreased by any converter. Removing a digit choose coordinates (150.6,120.8),(109.6,120.8),(150.6,53.1),(109.6,53.1) and cut out the rectangle or paint it white with brush size 	lowest and/or layers pixel(3x3).
\item For "no dots centered aligned header": pixel coordinate for placing dot 406,106. Image size 873 x 555. Selected paintbrush tool( on left side) with black color and size 20.00 with 2. Hardness (51x51)( on right  side). Removing a digit choose coordinates (340.8,116.6) , (299.2,116.6) , (299.2,49.4) , (340.8,49.4) and cut out the rectangle or paint it white with brush size lowest and/or layers pixel(3x3).
\item 3. For "no dots centered aligned body": pixel coordinate for placing dot 404,261. Image size 871x 550. Selected paintbrush tool( on left side) with black color and size 20.00 with 2. Hardness (51x51)( on right side). Removing a digit choose coordinates (339,270),  (297,270), (297,203), (339,203) and cut out the rectangle or paint it white with brush size lowest and/or layers pixel(3x3).
\item 4. For "dots left aligned header": pixel coordinate for Removing dot 226,116. Image size 874x 558.Selected paintbrush tool( on left side) with black color and size 20.00 with 2. Hardness (51x51)( on right side) . Removing a digit choose coordinates (153,122.5), (111,122.5), (111,55.5), (153,55.5) and cut out the rectangle or paint it white with brush size lowest and/or layers pixel(3x3).
\item 5. For "dots centered aligned header": pixel coordinate for Removing dot 412x198. Image size 876x 538. Selected paintbrush tool( on left side) with black color and size 20.00 with 2. Hardness (51x51)( on right side). Removing a digit choose coordinates (339,205), (297,205), (297,137), (339,137) and cut out the rectangle or paint it white with brush size  lowest and/or layers pixel(3x3).
\item 6. For "dots centered aligned body": pixel coordinate for Removing dot 407x293. Image size 871 x 557.Selected paintbrush tool( on left side) with black color and size 20.00 with 2. Hardness (51x51)( on right side). Removing a digit choose coordinates (334,300), (292,300), (292,232), (334,232) and cut out the rectangle or paint it white with brush size lowest and/or layers pixel(3x3).

\item 7. For "dots centered aligned body": pixel coordinate for Removing dot choose coordinate 37,42 .Image size 81x81. Selected paintbrush tool( on left side) with black color and  Hardness (51x51)( on right side) except white dot size is smaller than 20 for obvious reasons. Removing a digit choose coordinates (26.5,33.4) , (26.5,43.2) , (31.2,43.2) , (31.2,33.4) and cut out the rectangle or paint it white with brush size lowest and/or layers pixel(3x3).
\item 8. For "no dots left aligned header": pixel coordinate for  placing dot 19,15. Image size 81x81. Selected paintbrush tool( on left side) with black color and  Hardness (51x51)( on right side)  except white dot  size is smaller than 20 for obvious reasons. Removing a digit choose coordinates (9.4,7.4) , (9.4,17.5) , (14.2,17.5) , (14.2,7.4) and cut out the rectangle or paint it white with brush size lowest and/or layers pixel(3x3).
\item 9. For "no dots centered aligned header": pixel coordinate for placing dot 37,15 .Image size 81x81. Selected paintbrush tool( on left side) with black color and  Hardness (51x51)( on right side) except white dot size is smaller than 20 for obvious reasons. Removing a digit choose coordinates (27.4,7.5),(27.4,17.5),(31.6,17.5),(31.1,7.5) and cut out the rectangle or paint it white with brush size lowest and/or layers pixel(3x3).
\item 10. For "no dots centered aligned body": pixel coordinate for placing dot 37,37 . Image size 81x81. Selected paintbrush tool( on left side) with black color and  Hardness (51x51)( on right side)  except white dot size is smaller than 20 for obvious reasons. Removing a digit choose coordinates (27.4,29.5),(27.4,39.5),(31.5,39.5),(30.4,29.5) and cut out the rectangle or paint it white with brush size 	lowest and/or layers pixel(3x3).
\item 11. For "dots left aligned header": pixel coordinate for Removing dot 20,16 .Image size 81x81. Selected paintbrush tool( on left side) with black color and  Hardness (51x51)( on right side)  except white dot size is smaller than 20 for obvious reasons. Removing a digit choose coordinates (13.5,17.4),(13.5,8.4),(10.4,8.4),(10.4,17.4) and cut out the rectangle or paint it white with brush size lowest and/or layers pixel(3x3).
\item 12. For "dots centered aligned header": pixel coordinate for Removing dot 37,29 .Image size 81x81. Selected paintbrush tool( on left side) with black color and  Hardness (51x51)( on right side) except white dot size is smaller than 20 for obvious reasons. Removing a digit choose coordinates (31.6,30.4),(31.6,20.4),(27.4,20.4),(27.4,30.4) and cut out the rectangle or paint it white with brush size 	lowest and/or layers pixel(3x3).
\item 13. For all the small images it was unable to locate on GIMP but it is very easy to do in any Editor/Compiler in which one is working on because it's small.
\item 14. For "alice body centered 891 x 553 ": Removing a letter “ A  from alice “choose coordinates (337,292) , (276,292) , (276,223), (337,223) and cut out the rectangle or paint it white with brush size lowest , color white and/or layers pixel(3x3). For replacing Alice to Slice firstly remove A above method and then select Alphabetical tool in GIMP and draw a rectangle of same size and write letter S on it, make sure size is equal to other letters.
\item 15. For " alice header left 890 x 552":Removing a letter “ A from alice “ choose coordinates (162,119) , (100,119) , (100,53) , (162,53) and cut out the rectangle or paint it white with brush size lowest  , color white and/or layers pixel(3x3).For replacing Alice to Slice firstly remove A above method and then select Alphabetical tool in GIMP and draw a rectangle of same size and write letter S on it, make sure size is equal to other letters.
\item 15. For "alice body centered 15 x 15 ": For all the small images it was unable to locate on GIMP but it is very easy to do in any Editor/Compiler in which one is working on because it's small.
\item 16. For " alice header left 15x15 ":For all the small images it was unable to locate on GIMP but it is very easy to do in any Editor/Compiler in which one is working on because it's small.
\item 17. For "alice body centered 81x81 ": Removing a letter “ A  from alice “choose coordinates (31.8,43.6) , (24.3,43.6) , (24.3,33) , (31.8,33) and cut out the rectangle or paint it white with brush size lowest , color white and/or layers pixel(3x3).
\item 18.  For " alice header left 81x81 ":Removing a letter “ A from alice “ choose coordinates (15.8,17.8) , (8.4,17.8) , (8.4,11) , (15.8,11) and cut out the rectangle or paint it white with brush size lowest  , color white and/or layers pixel(3x3).

\end{itemize}

P.S: Numbers used are the part of the name of the image in git folder.
\end{document}